Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-10-19 src/tf-cutcell-comparison/fig-gravityWaves-theta.tex
annotate gravityWave figures

\documentclass{article}
\usepackage{showframe}
\usepackage[paperwidth=6.4in,paperheight=8.3in,margin=0in]{geometry}
\usepackage{mathptmx}%{times}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[absolute,overlay]{textpos}
\usepackage{color}

\setlength{\parindent}{0pt}
\begin{document}
\centering
\includegraphics[width=6in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffOverview.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-300dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-250dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-250dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-200dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-200dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-150dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-150dz/18000/thetaDiffMountain.pdf}
\end{document}

>>>>

\documentclass{article}
\usepackage{showframe}
\usepackage[paperwidth=6.2in,paperheight=5.6in,margin=0in]{geometry}
\usepackage{mathptmx}%{times}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[absolute,overlay]{textpos}
\usepackage{color}

\setlength{\parindent}{0pt}
\begin{document}
\TPMargin{3pt}
\textblockcolour{white}
\begin{textblock}{0.75}(1.4,0.5)
	\normalsize
	\centering
	(a)
\end{textblock}
\begin{textblock}{0.75}(1.2,6.5)
	\normalsize
	\centering
	(b)
\end{textblock}
\begin{textblock}{0.75}(9.05,6.5)
	\normalsize
	\centering
	(c)
\end{textblock}
\begin{textblock}{0.75}(1.2,11.3)
	\normalsize
	\centering
	(d)
\end{textblock}
\begin{textblock}{0.75}(9.05,11.3)
	\normalsize
	\centering
	(e)
\end{textblock}
\centering
\includegraphics[width=6in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffOverview.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-300dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-btf-250m-300dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-300dz/18000/tracerDiffMountain.pdf}

\newpage

250m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-250dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-250dz/18000/thetaDiffMountain.pdf}

250m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-250dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-250dz/18000/tracerDiffMountain.pdf}

\newpage
200m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-200dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-200dz/18000/thetaDiffMountain.pdf}

200m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-200dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-200dz/18000/tracerDiffMountain.pdf}

\newpage

150m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-150dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-150dz/18000/thetaDiffMountain.pdf}

150m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-150dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-150dz/18000/tracerDiffMountain.pdf}
\end{document}
